msuRACiFits_fits_rice_params

### 2025-05-07 CO2_response_fitting/Scripts/msuRACiFit_rice_params.Rmd
Update and rename 03_msuRACiFit_rice.Rmd to msuRACiFit_rice_params.Rmd

### Install A/Ci fitting package if necessary

## msuRACiFit

@@

OR

@@

### Load the msuRACiFit and readxl libraries:

```{r}
library(readxl)
library(msuRACiFit)
```

### Import excel data from the original file:

```{r}
#gas_exchange_data <- read_excel("Data/Gas_exchange_measurement_WT_plants.xls")
# ABSOLUTE PATH
gas_exchange_data <- read_excel("C:/Users/xxxx/Data/Gas_exchange_measurement_WT_plants.xls")
```

#### OR load each dataset as a separate file:

```{r}
#A330502WT1 <- read_excel("Data/IR64-A009-07-33-05-02_Wildtype1.xlsx")
#A330502WT2 <- read_excel("Data/IR64-A009-07-33-05-02_Wildtype2.xlsx")
#A330504WT1 <- read_excel("Data/IR64-A009-07-33-05-04_Wildtype1.xlsx")
#A330504WT2 <- read_excel("Data/IR64-A009-07-33-05-04_Wildtype2.xlsx")
#A330506WT1 <- read_excel("Data/IR64-A009-07-33-05-06_Wildtype1.xlsx")
#A330506WT2 <- read_excel("Data/IR64-A009-07-33-05-06_Wildtype2.xlsx")
#A330509WT1 <- read_excel("Data/IR64-A009-07-33-05-09_Wildtype1.xlsx")
#A330509WT2 <- read_excel("Data/IR64-A009-07-33-05-09_Wildtype2.xlsx")

#ABSOLUTE PATHS
A330502WT1 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-02_Wildtype1.xlsx")
A330502WT2 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-02_Wildtype2.xlsx")
A330504WT1 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-04_Wildtype1.xlsx")
A330504WT2 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-04_Wildtype2.xlsx")
A330506WT1 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-06_Wildtype1.xlsx")
A330506WT2 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-06_Wildtype2.xlsx")
A330509WT1 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-09_Wildtype1.xlsx")
A330509WT2 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-09_Wildtype2.xlsx")

```

### Append datasets in a list:

@@

### Calculate Gamma Star at diff temperatures, we use the function

@@

#### The tool uses preset in-vitro values from Hermida-Carrera et al (2016), where everything is presented in ppm, except for N. tabacum and A. thaliana.

##### Since we are analyzing the A/Ci in Pa, we have to adjust the resulting Gamma\*, Kc and Ko that we get in ppm to Pa before running calculations.

#### So, the $c$ and $\Delta H_a$ for gamma\* presented in the app/ preset table are for ppm, \#' and gamma\* is corrected \# as follows: gamma(Pa) = gamma(ppm) \* 1000 / 1000000 \* patm, \#' Kc (Pa) = Kc(umol mol -1) \* 1000 / 1000000 \* patm, \#' Kcair (Pa) = Kcair(umol mol -1) \* 1000 / 1000000 \* patm, \#' Ko (kPa) = O(Pa) / ((Kcair(Pa) / Kc(Pa)) - 1)/1000

### Create vectors of mean temperature and pressure

@@

### Call calcgammastar function with different temp inputs and get outputs saved in single vector for 8 files

```{r}
Gstars_rice<-msuRACiFit::calcGammaStar(13.7,24.6,mean_temps,21) #rice c and dHa 
```

### Next, we account for the variation in Press for each dataset and convert GammaStar back to Pa

@@

### Gamma Star at 25C differs for each file/dataset because the mean press differs

```{r}
Gstars_25_rice<-msuRACiFit::calcGammaStar(13.7,24.6,25,21)  
Gstars_25_Pa_rice<-Gstars_25_rice*(1000 / 1000000)*mean_press 
```

### Save these gamma star values

@@

```{r}
write(Gstars_25_Pa_rice,file="Outputs/Parameters/Gstars_25_Pa_rice.csv",sep=" ")
```

### To fit data using Shiny app, run

@@

### Select O.sativa as preset plant and copy in the average Tleaf and Pa for each curve

#### Generate guess and fit, saving output, png and table

#### Compare the fits found using complete sets of Sharkey's parameters for tobacco and Carmen's parameters for rice

#### 11/12/2023

#### We couldn't get a good estimate of Ko c and dHa via nls

#### (As it was fitted with near zero residuals, should not have converged)

##### It may be better to calculate a series of Ko values (one at each Tleaf) and pass them onto the fitting function

#### But first- calculate Kc and Kcair for our Tleaf values in umol mol-1 then convert them into Pa before working out Ko

#### Make sure all constants are named differently within the function to what they are called outside the function

### Load data containing kinetic parameters for rice

```{r}
param_data <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/Rubisco_kinetics_Oryza_sativa.xlsx")
```

### Import data for Kc_c and Kc_dHa

```{r}
Kc_c <- mean(na.omit(as.numeric(param_data$`c Kc (from μmolmol-1) (dimensionless)`))) 
Kc_dHa <- mean(na.omit(as.numeric(param_data$`DHA Kc (from μmolmol-1) (KJmol-1)`)))
```

### Import data for Kcair_c and Kcair_dHa

```{r}
Kcair_c <- mean(na.omit(as.numeric(param_data$`c Kcair (from μmolmol-1) (dimensionless)`))) 
Kcair_dHa <- mean(na.omit(as.numeric(param_data$`DHA Kcair (from μmolmol-1) (KJmol-1)`)))
```

### Write function to use the mean temperature in celsius from each curve for calculating Kc and Kcair

@@

### Create an empty dataframe to store all Kc and Kcair outputs

@@

### Loop through kinetic_params function, calculate Kc and Ko values at each temperature in mean_temps and convert values from ppm to Pa according to each mean_press

@@

### Append a column for calculating Ko from Kc and Kcair and converting these values to kPa

```{r}
all_param$Ko<-(21000 / ((all_param$Kcair / all_param$Kc) - 1))/1000 
all_param$Temperature <- mean_temps 
all_param$Press <- mean_press 
write.csv(all_param,file = "C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Outputs/Parameters/fitComplete/Rice/kinetic_parameters_rice.csv")
```

@@

### Initialise an empty list to store output of fitComplete

@@

### Fit curves individually using fitComplete algorithm

@@

### Save parameter outputs

```{r}
write.csv(completeFit1_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit1_console_rice_params.csv")
```

@@

### Save parameter outputs

```{r}
write.csv(completeFit2_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit2_console_rice_params.csv")
```

@@

### Save parameter

```{r}
write.csv(completeFit3_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit3_console_rice_params.csv")
```

@@

### Save parameter outputs

```{r}
write.csv(completeFit4_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit4_console_rice_params.csv")
```

@@

### Save parameter outputs

```{r}
write.csv(completeFit5_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit5_console_rice_params.csv")
```

@@

### Save parameter outputs

```{r}
write.csv(completeFit6_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit6_console_rice_params.csv")
```

@@

### Save parameter outputs

```{r}
write.csv(completeFit7_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit7_console_rice_params.csv")
```

@@

### Save parameter outputs

```{r}
write.csv(completeFit8_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit8_console_rice_params.csv")
```

## Produce data tables for each curve

@@

```

### Save data table

```{r}
write.csv(completeTables1_rice, file = "Outputs/Tables/fitComplete/Rice/completefit1_console_rice_dataTable.csv") 
```

`{SSR1<-sum(completeTables1_rice$res^2)}`

### Plot graph of limitations

```{r}
completeGraph1_rice <- reconstituteGraph(data=A330502WT1, 
                                         fitParams = completeFit1_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[1], 
                                         O2=21, 
                                         pressure=mean_press[(1)], 
                                         tleaf=mean_temps[(1)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[1, "Kc"], 
                                         Ko=all_param[1, "Ko"])
```

```{r}
#png("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Outputs/Graphs/fitComplete/Rice/completefits1_console_rice.png", width = 519, height = 457) 
plot(completeGraph1_rice) 
#dev.off()
```

completeTables2_rice \<- reconstituteTable(data=A330502WT2, fitParams = completeFit2_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[2], O2=21, pressure=mean_press[(2)], tleaf = mean_temps[(2)], ignoreTPU=F, Kc=all_param[2, "Kc"], Ko=all_param[2, "Ko"]) #Save data table write.csv(completeTables2_rice, file = "Outputs/Tables/fitComplete/Rice/completefit2_console_rice_dataTable.csv") SSR2\<-sum(completeTables2_rice\$`res^2`)

completeGraph2_rice \<- reconstituteGraph(data=A330502WT2, fitParams = completeFit2_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[2], O2=21, pressure=mean_press[(2)], tleaf=mean_temps[(2)], ignoreTPU=F, Kc=all_param[2, "Kc"], Ko=all_param[2, "Ko"])

@@

completeTables3_rice \<- reconstituteTable(data=A330504WT1, fitParams = completeFit3_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[3], O2=21, pressure=mean_press[(3)], tleaf = mean_temps[(3)], ignoreTPU=F, Kc=all_param[3, "Kc"], Ko=all_param[3, "Ko"]) #Save data table write.csv(completeTables3_rice, file = "Outputs/Tables/fitComplete/Rice/completefit3_console_rice_dataTable.csv") SSR3\<-sum(completeTables3_rice\$`res^2`)

completeGraph3_rice \<- reconstituteGraph(data=A330504WT1, fitParams = completeFit3_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[3], O2=21, pressure=mean_press[(3)], tleaf=mean_temps[(3)], ignoreTPU=F, Kc=all_param[3, "Kc"], Ko=all_param[3, "Ko"])

@@

completeTables4_rice \<- reconstituteTable(data=A330504WT2, fitParams = completeFit4_rice[[1]], name_assimilation = "Photo",name_ci=c("Ci"), gammastar=Gstars_Pa_rice[4], O2=21, pressure=mean_press[(4)], tleaf = mean_temps[(4)], ignoreTPU=F, Kc=all_param[4, "Kc"], Ko=all_param[4, "Ko"]) #Save data table write.csv(completeTables4_rice, file = "Outputs/Tables/fitComplete/Rice/completefit4_console_rice_dataTable.csv") SSR4\<-sum(completeTables4_rice\$`res^2`)

completeGraph4_rice \<- reconstituteGraph(data=A330504WT2, fitParams = completeFit4_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[4], O2=21, pressure=mean_press[(4)], tleaf=mean_temps[(4)], ignoreTPU=F, Kc=all_param[4, "Kc"], Ko=all_param[4, "Ko"]) png("Outputs/Graphs/fitComplete/Rice/completefits4_console_rice.png", width = 519, height = 457) plot(completeGraph4_rice) dev.off()

completeTables5_rice \<- reconstituteTable(data=A330506WT1, fitParams = completeFit5_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[5], O2=21, pressure=mean_press[(5)], tleaf = mean_temps[(5)], ignoreTPU=F, Kc=all_param[5, "Kc"], Ko=all_param[5, "Ko"]) #Save data table write.csv(completeTables5_rice, file = "Outputs/Tables/fitComplete/Rice/completefit5_console_rice_dataTable.csv") SSR5\<-sum(completeTables5_rice\$`res^2`)

completeGraph5_rice \<- reconstituteGraph(data=A330506WT1, fitParams = completeFit5_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[5], O2=21, pressure=mean_press[(5)], tleaf=mean_temps[(5)], ignoreTPU=F, Kc=all_param[5, "Kc"], Ko=all_param[5, "Ko"]) png("Outputs/Graphs/fitComplete/Rice/completefits5_console_rice.png", width = 519, height = 457) plot(completeGraph5_rice) dev.off()

completeTables6_rice \<- reconstituteTable(data=A330506WT2, fitParams = completeFit6_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[6], O2=21, pressure=mean_press[(6)], tleaf = mean_temps[(6)], ignoreTPU=F, Kc=all_param[6, "Kc"], Ko=all_param[6, "Ko"]) #Save data table write.csv(completeTables6_rice, file = "Outputs/Tables/fitComplete/Rice/completefit6_console_rice_dataTable.csv") SSR6\<-sum(completeTables6_rice\$`res^2`)

completeGraph6_rice \<- reconstituteGraph(data=A330506WT2, fitParams = completeFit6_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[6], O2=21, pressure=mean_press[(6)], tleaf=mean_temps[(6)], ignoreTPU=F, Kc=all_param[6, "Kc"], Ko=all_param[6, "Ko"])

@@

completeTables7_rice \<- reconstituteTable(data=A330509WT1, fitParams = completeFit7_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[7], O2=21, pressure=mean_press[(7)], tleaf = mean_temps[(7)], ignoreTPU=F, Kc=all_param[7, "Kc"], Ko=all_param[7, "Ko"]) #Save data table write.csv(completeTables7_rice, file = "Outputs/Tables/fitComplete/Rice/completefit7_console_rice_dataTable.csv") SSR7\<-sum(completeTables7_rice\$`res^2`)

completeGraph7_rice \<- reconstituteGraph(data=A330509WT1, fitParams = completeFit7_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[7], O2=21, pressure=mean_press[(7)], tleaf=mean_temps[(7)], ignoreTPU=F, Kc=all_param[7, "Kc"], Ko=all_param[7, "Ko"])

@@

completeTables8_rice \<- reconstituteTable(data=A330509WT2, fitParams = completeFit8_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[8], O2=21, pressure=mean_press[(8)], tleaf = mean_temps[(8)], ignoreTPU=F, Kc=all_param[8, "Kc"], Ko=all_param[8, "Ko"]) #Save data table write.csv(completeTables8_rice, file = "Outputs/Tables/fitComplete/Rice/completefit8_console_rice_dataTable.csv") SSR8\<-sum(completeTables8_rice\$`res^2`)

completeGraph8_rice \<- reconstituteGraph(data=A330509WT2, fitParams = completeFit8_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[8], O2=21,pressure=mean_press[(8)], tleaf=mean_temps[(8)], ignoreTPU=F, Kc=all_param[8, "Kc"], Ko=all_param[8, "Ko"]) png("Outputs/Graphs/fitComplete/Rice/completefits8_console_rice.png", width = 519, height = 457) plot(completeGraph8_rice) dev.off()

### Combine and save SSR

@@

### Export plot coordinates for limitations, example below (consider looping)

```{r}
Ac<-completeGraph1_rice$plot_env$cdat 
Aj<-completeGraph1_rice$plot_env$jdat 
Ap<-completeGraph1_rice$plot_env$pdat 
limitations <- list(Ac,Aj,Ap) 
write.csv(limitations,"Outputs/Tables/fitComplete/Rice/completeFit1_rice_limitations.csv")
```

>>>>

---
title: "msuRACiFits_fits_rice_params"
author: "Supreeta Vijayakumar"
date: "`r Sys.Date()`"
output: html_document
---

## Install A/Ci fitting package if necessary

msuRACiFit is a package of r scripts used to fit CO2 response curves developed by Thomas Sharkey's lab at Michigan State University.\
\
Source Code:\
<https://github.com/poales/msuRACiFit>

Publication:\
<https://doi.org/10.1111/pce.14153>

### Install the package using devtools:

@@

### or remotes:

@@

### Load the here, msuRACiFit and readxl libraries:

```{r}
library(here)
library(readxl)
library(msuRACiFit)
```

Using \`here' roots the file path to the project environment.

### Import Excel files containing gas exchange data:

```{r}
A330502WT1 <- read_excel(here("Data","IR64-A009-07-33-05-02_Wildtype1.xlsx"))
A330502WT2 <- read_excel(here("Data","IR64-A009-07-33-05-02_Wildtype2.xlsx"))
A330504WT1 <- read_excel(here("Data","IR64-A009-07-33-05-04_Wildtype1.xlsx"))
A330504WT2 <- read_excel(here("Data","IR64-A009-07-33-05-04_Wildtype2.xlsx"))
A330506WT1 <- read_excel(here("Data","IR64-A009-07-33-05-06_Wildtype1.xlsx"))
A330506WT2 <- read_excel(here("Data","IR64-A009-07-33-05-06_Wildtype2.xlsx"))
A330509WT1 <- read_excel(here("Data","IR64-A009-07-33-05-09_Wildtype1.xlsx"))
A330509WT2 <- read_excel(here("Data","IR64-A009-07-33-05-09_Wildtype2.xlsx"))
```

### Store the files in a list:

@@

### Calculate Gamma Star at different temperatures using calcGammaStar:

@@

The tool uses preset in-vitro values from Hermida-Carrera et al (2016), where everything is presented in ppm, except for N. tabacum and A. thaliana.

Since we are analyzing the A/Ci in Pa, we have to adjust the resulting Gamma\*, Kc and Ko that we get in ppm to Pa before running calculations.

$c$ and $\Delta H_a$ for Gamma\* presented in the app/ preset table are for ppm, and gamma\* is corrected as follows:\
\
Gamma\* (Pa) = Gamma\*(ppm) \* 1000 / 1000000 \* Patm,\
Kc (Pa) = Kc(umol mol -1) \* 1000 / 1000000 \* Patm\
Kcair (Pa) = Kcair(umol mol -1) \* 1000 / 1000000 \* Patm,\
Ko (kPa) = O(Pa) / ((Kcair(Pa) / Kc(Pa)) - 1)/1000

### Create vectors of mean temperature and pressure:

@@

### Call calcgammastar function with different temperature inputs and get outputs saved in single vector for 8 files:

```{r}
Gstars_rice<-msuRACiFit::calcGammaStar(13.7,24.6,mean_temps,21) #rice c and dHa 
Gstars_rice_25<-msuRACiFit::calcGammaStar(13.7,24.6,25,21) #rice c and dHa 
```

### Next, we account for the variation in Press for each dataset and converting GammaStar back to Pa:

@@

### Save these gamma star values in a .csv:

@@

### Alternatively, to fit data using the Shiny app, run:

@@

Select *O.sativa* as preset plant and fill in the average Tleaf and Pa for each curve, generating guesses and fits, saving outputs as .png and csv tables.

#### Calculate Kc and Kcair for our Tleaf values in umol mol-1 then convert them into Pa before working out Ko.

Make sure all constants are named differently within the function to what they are called outside the function.

### Import data for Kc_c and Kc_dHa:

```{r}
Kc_c <- 38.9
Kc_dHa <- 83.1
```

### Import data for Kcair_c and Kcair_dHa:

```{r}
Kcair_c <- 30.5 
Kcair_dHa <- 60.5
```

### Write function to use the mean temperature in celsius from each curve for calculating Kc and Kcair:

@@

### Create an empty dataframe to store all Kc and Kcair outputs:

@@

### Loop through kinetic_params function, calculate Kc and Ko values at each temperature in mean_temps and convert values from ppm to Pa according to each mean_press:

@@

### Append a column for calculating Ko from Kc and Kcair and converting these values to kPa:

```{r}
all_param$Ko<-(21000 / ((all_param$Kcair / all_param$Kc) - 1))/1000 
all_param$Temperature <- mean_temps 
all_param$Press <- mean_press 
write.csv(all_param,
         file = "Outputs/Parameters/fitComplete/Rice/kinetic_parameters_rice.csv")
```

@@

### Initialise an empty list to store output of fitComplete:

@@

### Fit curves individually using fitComplete algorithm:

@@

@@

@@

@@

@@

@@

@@

@@

### Save parameter outputs:

```{r}
write.csv(completeFit1_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit1_console_rice_params.csv")

write.csv(completeFit2_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit2_console_rice_params.csv")

write.csv(completeFit3_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit3_console_rice_params.csv")

write.csv(completeFit4_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit4_console_rice_params.csv")

write.csv(completeFit5_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit5_console_rice_params.csv")

write.csv(completeFit6_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit6_console_rice_params.csv")

write.csv(completeFit7_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit7_console_rice_params.csv")

write.csv(completeFit8_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit8_console_rice_params.csv")
```

## Produce data tables for each curve:

@@

completeTables2_rice <- reconstituteTable(data=A330502WT2, 
                                          fitParams = completeFit2_rice[[1]], 
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[2], 
                                          O2=21, 
                                          pressure=mean_press[(2)], 
                                          tleaf = mean_temps[(2)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[2, "Kc"],
                                          Ko=all_param[2, "Ko"])

completeTables3_rice <- reconstituteTable(data=A330504WT1, 
                                          fitParams = completeFit3_rice[[1]], 
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[3], 
                                          O2=21, 
                                          pressure=mean_press[(3)], 
                                          tleaf = mean_temps[(3)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[3, "Kc"], 
                                          Ko=all_param[3, "Ko"])

completeTables4_rice <- reconstituteTable(data=A330504WT2, 
                                          fitParams = completeFit4_rice[[1]], 
                                          name_assimilation = "Photo",
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[4], 
                                          O2=21, 
                                          pressure=mean_press[(4)], 
                                          tleaf = mean_temps[(4)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[4, "Kc"], 
                                          Ko=all_param[4, "Ko"])

completeTables5_rice <- reconstituteTable(data=A330506WT1, 
                                          fitParams = completeFit5_rice[[1]], 
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[5], 
                                          O2=21, 
                                          pressure=mean_press[(5)], 
                                          tleaf = mean_temps[(5)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[5, "Kc"], 
                                          Ko=all_param[5, "Ko"])

completeTables6_rice <- reconstituteTable(data=A330506WT2, 
                                          fitParams = completeFit6_rice[[1]], 
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[6], 
                                          O2=21, 
                                          pressure=mean_press[(6)], 
                                          tleaf = mean_temps[(6)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[6, "Kc"], 
                                          Ko=all_param[6, "Ko"])

completeTables7_rice <- reconstituteTable(data=A330509WT1, 
                                          fitParams = completeFit7_rice[[1]], 
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[7], 
                                          O2=21, 
                                          pressure=mean_press[(7)], 
                                          tleaf = mean_temps[(7)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[7, "Kc"], 
                                          Ko=all_param[7, "Ko"])

completeTables8_rice <- reconstituteTable(data=A330509WT2, 
                                          fitParams = completeFit8_rice[[1]], 
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[8], 
                                          O2=21, 
                                          pressure=mean_press[(8)], 
                                          tleaf = mean_temps[(8)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[8, "Kc"], 
                                          Ko=all_param[8, "Ko"])
```

### Save data tables:

```{r}
write.csv(completeTables1_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit1_console_rice_dataTable.csv") 
write.csv(completeTables2_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit2_console_rice_dataTable.csv")
write.csv(completeTables3_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit3_console_rice_dataTable.csv") 
write.csv(completeTables4_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit4_console_rice_dataTable.csv")
write.csv(completeTables5_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit5_console_rice_dataTable.csv")
write.csv(completeTables6_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit6_console_rice_dataTable.csv") 
write.csv(completeTables7_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit7_console_rice_dataTable.csv")
write.csv(completeTables8_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit8_console_rice_dataTable.csv") 
```

### Plot graphs of limitations:

```{r}
completeGraph1_rice <- reconstituteGraph(data=A330502WT1, 
                                         fitParams = completeFit1_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[1], 
                                         O2=21, 
                                         pressure=mean_press[(1)], 
                                         tleaf=mean_temps[(1)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[1, "Kc"], 
                                         Ko=all_param[1, "Ko"])

completeGraph2_rice <- reconstituteGraph(data=A330502WT2, 
                                         fitParams = completeFit2_rice[[1]], 
                                         name_assimilation="Photo", name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[2], O2=21, 
                                         pressure=mean_press[(2)], tleaf=mean_temps[(2)], 
                                         ignoreTPU=F,
                                         Kc=all_param[2, "Kc"], 
                                         Ko=all_param[2, "Ko"])

completeGraph3_rice <- reconstituteGraph(data=A330504WT1, 
                                         fitParams = completeFit3_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[3], 
                                         O2=21, 
                                         pressure=mean_press[(3)], 
                                         tleaf=mean_temps[(3)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[3, "Kc"], 
                                         Ko=all_param[3, "Ko"])

completeGraph4_rice <- reconstituteGraph(data=A330504WT2, 
                                         fitParams = completeFit4_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[4],
                                         O2=21, 
                                         pressure=mean_press[(4)], 
                                         tleaf=mean_temps[(4)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[4, "Kc"], 
                                         Ko=all_param[4, "Ko"])

completeGraph5_rice <- reconstituteGraph(data=A330506WT1, 
                                         fitParams = completeFit5_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[5],
                                         O2=21, 
                                         pressure=mean_press[(5)], 
                                         tleaf=mean_temps[(5)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[5, "Kc"], 
                                         Ko=all_param[5, "Ko"])

completeGraph6_rice <- reconstituteGraph(data=A330506WT2, 
                                         fitParams = completeFit6_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[6],
                                         O2=21, 
                                         pressure=mean_press[(6)], 
                                         tleaf=mean_temps[(6)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[6, "Kc"], 
                                         Ko=all_param[6, "Ko"])

completeGraph7_rice <- reconstituteGraph(data=A330509WT1, 
                                         fitParams = completeFit7_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[7],
                                         O2=21, 
                                         pressure=mean_press[(7)], 
                                         tleaf=mean_temps[(7)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[7, "Kc"], 
                                         Ko=all_param[7, "Ko"])

completeGraph8_rice <- reconstituteGraph(data=A330509WT2, 
                                         fitParams = completeFit8_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[8],
                                         O2=21,
                                         pressure=mean_press[(8)], 
                                         tleaf=mean_temps[(8)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[8, "Kc"], 
                                         Ko=all_param[8, "Ko"]) 
```

### Save plots:

```{r}
png("Outputs/Graphs/fitComplete/Rice/completefits1_console_rice.png", width = 519, height = 457) 
plot(completeGraph1_rice) 
dev.off()

@@

@@

png("Outputs/Graphs/fitComplete/Rice/completefits4_console_rice.png", width = 519, height = 457) 
plot(completeGraph4_rice) 
dev.off()

png("Outputs/Graphs/fitComplete/Rice/completefits5_console_rice.png", width = 519, height = 457) 
plot(completeGraph5_rice) 
dev.off()

@@

@@

png("Outputs/Graphs/fitComplete/Rice/completefits8_console_rice.png", width = 519, height = 457) 
plot(completeGraph8_rice) 
dev.off()
```

#### Calculate sum of squared residuals:

```{r}
SSR1<-sum(completeTables1_rice$res^2)
SSR2<-sum(completeTables2_rice$res^2)
SSR3<-sum(completeTables3_rice$res^2)
SSR4<-sum(completeTables4_rice$res^2)
SSR5<-sum(completeTables5_rice$res^2)
SSR6<-sum(completeTables6_rice$res^2)
SSR7<-sum(completeTables7_rice$res^2)
SSR8<-sum(completeTables8_rice$res^2)
```

### Combine and save SSR values:

@@

### Export plot coordinates for limitations, example below:

```{r}
Ac<-completeGraph1_rice$plot_env$cdat 
Aj<-completeGraph1_rice$plot_env$jdat 
Ap<-completeGraph1_rice$plot_env$pdat 
limitations <- list(Ac,Aj,Ap)

write.csv(limitations,"Outputs/Tables/fitComplete/Rice/completeFit1_rice_limitations.csv")
```
